|

### 2022-11-07 manuscript.Rmd
more bib
put some lit on the back burner

## @koAccessComputingPromotesTeaching2016#

## ### Findings

@@

@@

>>>>

@@

<!-- Three types of major disabilities  affected by inaccessible viz -->
> There are three main kinds of disability that may affect access to visualizations: visual, cognitive, and motor impairments. It is not uncommon for people to have more than one kind of impairment.

@@

<!-- critical disability studies -->
@mankoffDisabilityStudiesSource2010

<!-- The following is good to review when having more time -->

## @koAccessComputingPromotesTeaching2016
